%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer 2} % Job title
    {Flipkart} % Organization
    {Bengaluru, Karnataka} % Location
    {June 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to the \textbf{Product Exchange} platform powering end-to-end exchange flows and return lifecycle across Flipkart's core ecosystem, supporting high-scale production traffic.}
        \item {Built real-time monitoring and alerting using \textbf{Grafana} and \textbf{Prometheus} for \textbf{microservices}, improving incident detection time and reducing service downtime risk.}
        \item {Reduced \textbf{API} latency by approximately 80\% (120ms to 20ms) by implementing \textbf{Caffeine} caching and optimizing \textbf{POJO} design, significantly improving response times for high-frequency endpoints.}
        \item {Designed and implemented ``Externalization'' feature to enable third-party partners (e.g., SAMSUNG) to leverage Flipkart's product exchange capabilities.}
        \item {Built scalable \textbf{REST APIs} and \textbf{Quartz} scheduler-based batch jobs to generate and deliver serviceable pincode datasets to external clients and provide dynamic pricing data files for product exchange valuation.}
        \item {Improved system efficiency and partner integration readiness by automating overnight batch processing workflows for data delivery.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Technology Associate} % Job title
    {Morgan Stanley} % Organization
    {Bengaluru, Karnataka} % Location
    {Jan. 2024 - May 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led efforts to scale the trading application to handle orders from all asset classes, navigating complex requirements and edge cases.}
        \item {Implemented \textbf{metrics} for system health and alert conditions, wired into \textbf{Prometheus} alerting so production issues surfaced reliably to on-call engineers.}
        \item {Integrated \textbf{SQL} and \textbf{DB2} stored procedures to streamline data management and processing for trading workflows.}
        \item {Built \textbf{REST APIs} and implemented logic for a model portal where external managers and finance managers authored client-specific models; automated recurring operations with \textbf{Autosys} and connected services to the \textbf{UI}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technology Associate} % Job title
    {Morgan Stanley} % Organization
    {Bengaluru, Karnataka} % Location
    {Jan. 2023 - Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded initialization and delivery of a trading application on \textbf{Spring Boot}.}
        \item {Designed and implemented asset-class-aware order routing to improve throughput and correctness.}
        \item {Modernized a legacy stack into distributed \textbf{Java} \textbf{microservices} using \textbf{SQL}, \textbf{DB2}, and \textbf{Drools}; introduced \textbf{parallel processing}, \textbf{multithreading}, and \textbf{daemon processes}, raising order execution and routing capacity from approximately 20k to 80k orders per minute.}
        \item {Integrated \textbf{IBM MQ} and \textbf{Kafka} for order processing and asynchronous messaging across services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technology Analyst} % Job title
    {Morgan Stanley} % Organization
    {Bengaluru, Karnataka} % Location
    {Aug. 2022 - Jan. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built \textbf{Spring Boot} components supporting fractional-share trading flows.}
        \item {Embedded the \textbf{Drools} rules engine for trading logic, improving consistency and maintainability of order decisions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern Project} % Job title
    {3DR Explain, Morgan Stanley} % Organization
    {Bengaluru, Karnataka} % Location
    {Jan. 2022 - June 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a full-stack application using \textbf{React} and \textbf{Flask} (\textbf{Python}) during internship.}
        \item {Implemented sorting for \textbf{Apache SOLR}-fetched articles by short title, title, short description, topics, and tag types, improving content discoverability and user experience.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
